### 2025-02-26 paper/paper.tex
te

\begin{table}[H]
  \centering
  \caption{シミュレーション条件の例}
  \label{tab:sim-param}
  \begin{tabular}{c|@{\hspace{1.8em}}l}
    \hline
    パラメータ & 値・例 \\
    \hline
    シミュレーション時間 & 60 \, \,$\mathrm{s}$\, \\
    モード & \,``a" \\
    スロット時間 (802.11a) & \, 9 \, \,$\mathrm{\mu s}$\, \\
    DIFS (802.11a) & 34 \, \,$\mathrm{\mu s}$\, \\
    SIFS (802.11a) & 16 \, \,$\mathrm{\mu s}$\, \\
    伝送レート & 24 \, \,Mbps\, \\
    端末数 & 80 \, \,台\, \\
    \hline
  \end{tabular}
\end{table}

@@

\begin{table}[H]
  \centering
  \caption{シミュレーション1パラメータ}
  \label{tab:sim1-param}
  \begin{tabular}{c|@{\hspace{1.8em}}l}
    \hline
    パラメータ & 値・例 \\
    \hline
    シミュレーション時間 & 60 \, \,$\mathrm{s}$\, \\
    モード & \,``a" \\
    スロット時間 (802.11a) & \, 9 \, \,$\mathrm{\mu s}$\, \\
    DIFS (802.11a) & 34 \, \,$\mathrm{\mu s}$\, \\
    SIFS (802.11a) & 16 \, \,$\mathrm{\mu s}$\, \\
    伝送レート & 24 \, \,Mbps\, \\
    端末数 & 1～80 \, \,台\, \\
    \hline
  \end{tabular}
\end{table}

@@

\begin{table}[H]
  \centering
  \caption{シミュレーション1パラメータ}
  \label{tab:sim2-param}
  \begin{tabular}{c|@{\hspace{1.8em}}l}
    \hline
    パラメータ & 値・例 \\
    \hline
    シミュレーション時間 & 60 \, \,$\mathrm{s}$\, \\
    モード & \,``a" \\
    スロット時間 (802.11a) & \, 9 \, \,$\mathrm{\mu s}$\, \\
    DIFS (802.11a) & 34 \, \,$\mathrm{\mu s}$\, \\
    SIFS (802.11a) & 16 \, \,$\mathrm{\mu s}$\, \\
    伝送レート & 6～54 \, \,Mbps\, \\
    端末数 & 1～80 \, \,台\, \\
    \hline
  \end{tabular}
\end{table}

>>>>

\begin{table}[H]
  \centering
  \caption{シミュレーション条件の例}
  \label{tab:sim-param}
  \begin{tabular}{c|@{\hspace{1.8em}}l}
    \hline
    パラメータ & 値・例 \\
    \hline
    シミュレーション時間 & 60 \, \,$\mathrm{s}$\, \\
    モード & \, \,  a \\
    スロット時間 (802.11a) & \, 9 \, \,$\mathrm{\mu s}$\, \\
    DIFS (802.11a) & 34 \, \,$\mathrm{\mu s}$\, \\
    SIFS (802.11a) & 16 \, \,$\mathrm{\mu s}$\, \\
    伝送レート & 24 \, \,Mbps\, \\
    端末数 & 80 \, \,台\, \\
    \hline
  \end{tabular}
\end{table}

@@

\begin{table}[H]
  \centering
  \caption{シミュレーション1パラメータ}
  \label{tab:sim1-param}
  \begin{tabular}{c|@{\hspace{1.8em}}l}
    \hline
    パラメータ & 値・例 \\
    \hline
    シミュレーション時間 & 60 \, \,$\mathrm{s}$\, \\
    モード & \, \,  a \\
    スロット時間 (802.11a) & \, 9 \, \,$\mathrm{\mu s}$\, \\
    DIFS (802.11a) & 34 \, \,$\mathrm{\mu s}$\, \\
    SIFS (802.11a) & 16 \, \,$\mathrm{\mu s}$\, \\
    伝送レート & 24 \, \,Mbps\, \\
    端末数 & 1～80 \, \,台\, \\
    \hline
  \end{tabular}
\end{table}

@@

\begin{table}[H]
  \centering
  \caption{シミュレーション1パラメータ}
  \label{tab:sim2-param}
  \begin{tabular}{c|@{\hspace{1.8em}}l}
    \hline
    パラメータ & 値・例 \\
    \hline
    シミュレーション時間 & 60 \, \,$\mathrm{s}$\, \\
    モード & \, \,  a \\
    スロット時間 (802.11a) & \, 9 \, \,$\mathrm{\mu s}$\, \\
    DIFS (802.11a) & 34 \, \,$\mathrm{\mu s}$\, \\
    SIFS (802.11a) & 16 \, \,$\mathrm{\mu s}$\, \\
    伝送レート & 6～54 \, \,Mbps\, \\
    端末数 & 1～80 \, \,台\, \\
    \hline
  \end{tabular}
\end{table}
